Supplementary Material \\

### 2021-12-16 paper.tex
Updates from Overleaf

%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set, whereas the restrictions set in the intuitive approach proved suitable. All models for the intuitive approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs. All three approaches and all ML models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set. The restrictions set in the intuitive approach, on the other hand, which relies exclusively on findings from the literature, proved more suitable.  
All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials to a probability of $>50 \ \%$. 
All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates (to a probability of $>XX \ \%$) of $8$ elemental, $29$ binary, and $10$ tertiary compounds.

@@

\subsubsection*{The Ferrenti approach}
The first approach to defining a training set is based on the criteria from the paper by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials from the Materials Project. In this framework, we label \textbf{suitable} candidates by the following steps. 
\begin{enumerate}
    \item Include materials that;
    \begin{itemize}
        \item contain elements with more than $50 \ \%$ natural abundance of spin zero  isotopes,
        \item crystallize in non-polar space groups,
        \item are present in the ICSD database, and
        \item are calculated to be nonmagnetic. 
    \end{itemize}
    \item Pragmatically remove toxic, radioactive and otherwise ``difficult'' materials;
    \begin{itemize}
        \item exclude Th, U, Cd and Hg because they are radioactive and/or toxic in most stable forms,
        \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
        \item exclude transition metal elements with unpaired electrons like Ru, Os, Fe or Ni because of their paramagnetism.
    \end{itemize}
    \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional. The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations. 
    \item Ensure that energy above hull is less than $0.2$~eV per atom.
\end{enumerate}

@@

The following steps constitute the process of choosing \textbf{suitable} candidates 
in the \emph{augmented Ferrenti approach}. 
\begin{enumerate}
    \item Include materials that; 
    \begin{itemize}
        \item contain elements where more than half have a natural abundance of zero spin isotopes, except Al, P, Ga, As, B and N, 
        \item crystallize in non-polar space groups,
        \item are present in the ICSD database,
        \item are calculated to be nonmagnetic. 
    \end{itemize}
    \item Only keep materials that have a band gap larger than $1.5$~eV as calculated by PBE-GGA. The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid including an unfeasible number of candidate materials. 
    \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
\end{enumerate}

@@

The number of candidates predicted by each of the four machine learning methods 'Logistic regression', 'Decision trees', 'Random forests' and 'Gradient boosting' is labeled in Figure~\ref{fig:predictions}(a) for the Ferrenti approach. 
From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates. All four methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with the probability similar to a coin flip. 
If we were to raise the minimum bar of a prediction to $70 \ \%$ instead of $50 \ \%$, the above ML algorithms would only agree on around $3000$ suitable candidates. 
We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the training set. 
This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our ML methods. 
%Be careful here - PBE is known for underestimating band gaps. 
For example, the ML methods do not maintain the band gap restriction from the training set definition. 
Ideally, we would expect that the ML methods would have probabilities lower than $50 \ \%$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case. 
We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein, 
indicating that the band gap restriction is not recognized as important by the machine learning algorithms. 
Small band gaps could make it challenging to facilitate deep level defects. 
On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for some of the materials.

@@

@@

>>>>

%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set, whereas the restrictions set in the intuitive approach proved suitable. All models for the intuitive approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs. All three approaches and all ML models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set. The restrictions set in the intuitive approach, on the other hand, which relies exclusively on findings from the literature, proved more suitable.  
All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials to a probability of $>50 \ \%$. 
All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates (to a probability of $>50 \ \%$) of $8$ elemental, $29$ binary, and $10$ tertiary compounds.

@@

\subsubsection*{The Ferrenti approach}
The first approach to defining a training set is based on the criteria from the paper by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials from the Materials Project. In this framework, we label \textbf{suitable} candidates by the following steps. 
\begin{enumerate}
    \item Include materials that;
    \begin{itemize}
        \item contain elements with more than $50 \ \%$ natural abundance of spin zero  isotopes,
        \item crystallize in non-polar space groups,
        \item are present in the ICSD database, and
        \item are calculated to be nonmagnetic. 
    \end{itemize}
    \item Pragmatically remove toxic, radioactive and otherwise ``difficult'' materials;
    \begin{itemize}
        \item exclude Th, U, Cd and Hg because they are radioactive and/or toxic in most stable forms,
        \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism. Ru and Os are also removed because they only exist in the data as complex cluster structures. 
    \end{itemize}
    \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional. The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations. 
    \item Ensure that energy above hull is less than $0.2$~eV per atom.
\end{enumerate}

@@

The following steps constitute the process of choosing \textbf{suitable} candidates 
in the \emph{augmented Ferrenti approach}. 
\begin{enumerate}
    \item Include materials that; 
    \begin{itemize}
        \item contain elements where more than half have a natural abundance of zero spin isotopes, including Al, P, Ga, As, B and N, 
        \item crystallize in non-polar space groups,
        \item are present in the ICSD database,
        \item are calculated to be nonmagnetic. 
    \end{itemize}
    \item Only keep materials that have a band gap larger than $1.5$~eV as calculated by PBE-GGA. The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid including an unfeasible number of candidate materials. 
    \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
\end{enumerate}

@@

The number of candidates predicted by each of the four machine learning methods 'Logistic regression', 'Decision trees', 'Random forests' and 'Gradient boosting' is labeled in Figure~\ref{fig:predictions}(a) for the Ferrenti approach. 
From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates. All four methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with the probability similar to a coin flip. 
If we were to raise the minimum bar of a prediction to $70 \ \%$ instead of $50 \ \%$, the above ML algorithms would only agree on $1784$ suitable candidates. 
We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the training set. 
This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our ML methods. 
%Be careful here - PBE is known for underestimating band gaps. 
For example, the ML methods do not maintain the band gap restriction from the training set definition. 
Ideally, we would expect that the ML methods would have probabilities lower than $50 \ \%$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case. 
We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein, 
indicating that the band gap restriction is not recognized as important by the machine learning algorithms. 
Small band gaps could make it challenging to facilitate deep level defects. 
On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for some of the materials.

@@

\begin{figure}[h] %!tbp
    \centering
    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
        \input{figures/histograms/summary-01-02-histogram-.tex}
    \end{subfigure}%

    \begin{subfigure}{1\textwidth}
        \centering
        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
        \input{figures/histograms/summary-03-histogram-.tex}
    \end{subfigure}
    \caption{Histograms of predicted materials as a function of band gaps, where all models in an approach agree with at least the probability of $50\%$. The number of predicted materials are $6804$ for the Ferrenti approach, $9227$ for the augmented Ferrenti approach, and $214$ for the intuitive approach.}
    \label{fig:histogram}
\end{figure}

@@

\begin{table}[b]
    \centering 
    \caption{Overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree. A probability of $50 \ \%$ represents the confidence of a coin flip, while $100 \ \%$ is a fully confident prediction.}
    \begin{tabular}{c|c|c|c}
      & $50 \ \%$ & $75 \ \%$ & $85 \ \%$ \\
     \hline
     Ferrenti approach &  $6804$ & $1784$ & $258$  \\
     Augmented Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
     Intuitive approach & $214$ & $66$ & $9$ \\
     \hline
     All approaches together & $47$ & $6$ & 0 \\
    \end{tabular}
    \label{tab:probabilites}
\end{table}

### 2021-12-16 supplementary.tex
Updates from Overleaf

\title{Supplementary Material \\ 
Predicting Solid State Qubit Candidates}

\author{Oliver Lerst{\o}l Hebnes}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}

@@

\subsection*{Optimization of machine learning models}
Morten/Oliver please add details.

\section*{Supplementary results}
Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all four machine learning models, using the data set derived in the intuitive approach, agreed on with more than $75 \ \%$ probability.  All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional. Note that materials can appear several times  on  the  list due  to  different  structures of the same composition. The  list  contains five elementary (unary), 46  binary and  15 ternary compounds.

@@

>>>>

\title{Supplementary Material \\ 
%Predicting Solid State Qubit Candidates}
Predicting Solid State Material Platforms for Quantum Technologies}

\author{Oliver Lerst{\o}l Hebnes}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\affiliation{Sopra Steria, N-0185 Oslo, Norway}

@@

\subsection*{Optimization of machine learning models}

\section*{Supplementary results}
Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all four machine learning models, using the data set derived in the intuitive approach, agreed on with more than $75 \ \%$ probability.  All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional. Note that materials can appear several times  on  the  list due  to  different  structures of the same composition. The  list  contains $5$ elementary (unary), $46$  binary and  $15$ ternary compounds.

@@

Still missing.
